---
title: "Markdown Report"
author: "Elisabetta Minguzzi"
date: "2024-01-09"
output: html_document
---

# My first markdown document!

Here you can add some text if you want!
# Knit in HTML on R --> save file

In this case you attain a result:
```{r, eval=TRUE}    
2 + 3
```

In this case, you do not:
```{r,eval=FALSE}
2 + 3
```

Using proper packages; the imageRy package has been built at Alma Mater for learning remote sensing:
```{r,eval=TRUE}
library(imageRy)
```

Let's import some data by listing these in imageRy:
```{r,eval=TRUE}
imlist()
```


Importing the Mato grosso area image without warnings: 
```{r,eval=TRUE, warning=FALSE}
mato1992 <- im.import("matogrosso_15_1992219_lrg.jpg")
```

Making a new plot of the Mato Grosso area with NIR on top of the green component of the RGB space: 
```{r,eval=TRUE}
im.plotRGB(mato1992, r=2, g=1, b=3)
```

Plotting several images altogether: 
```{r,eval=TRUE}
par(mfrow=c(2,2))
im.plotRGB(mato1992, r=1, g=2, b=3)
im.plotRGB(mato1992, r=2, g=1, b=3)
im.plotRGB(mato1992, r=3, g=2, b=1)
im.plotRGB(mato1992, r=1, g=3, b=2)
```

Calculating spectral indices: 
```{r,eval=TRUE}
library(viridis)
library(terra)
dvi <- mato1992[[1]]-mato1992[[2]]
viridisc <- colorRampPalette(viridis(7)) (255)
plot(dvi, col=viridisc)
```
Calculating variability:
```{r,eval=TRUE}
sd5 <- focal(mato1992[[1]], matrix(1/25,5,5), fun=sd)
plot(sd5, col=viridisc)
```
